---
title: "Experiment: Flipping a fair coin (R Simulated)"
output: html_notebook
---

```{r include=FALSE}
library(tidyverse)
library(reshape2)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

```

For this experiment we will flip a fair coin 20 times and count the number of times it lands on heads. At such a low number of observations we would expect to see a good amount of variability from the mean value of 10. To measure this variability we will take 5 samples.

We will then repeat the experiment again with a much higher number of observations (50). We expect that our mean head count will be much closer to the expected value by due to decreased variability.

#Analysis of flipping a fair coin twenty times.

```{r}
df <- tibble(n = seq(1:20),
             sample1 = rbinom(20, 1, 0.5),
             sample2 = rbinom(20, 1, 0.5),
             sample3 = rbinom(20, 1, 0.5),
             sample4 = rbinom(20, 1, 0.5),
             sample5 = rbinom(20, 1, 0.5))

knitr::kable(df, align = c('c','c','c','c','c','c'), format="pandoc", caption = "Table of Results (0 = Tails, 1 = Heads)")
```

### Sample Statistics

```{r}
groupdf <- melt(df[c("sample1","sample2","sample3","sample4","sample5")], variable.name = "samplen", id.vars = 0)

ggplot(groupdf, mapping = aes(samplen, value)) + geom_bar(stat = "identity", fill = "steelblue") + labs(x=NULL, y="Number of Heads", title = "Head Counts per Sample") + geom_hline(yintercept = 10, colour = "light gray", size = 1) + theme_minimal()

summary(df[2:6])
```


```{r}
sampledf <- tibble(n = seq(1:5),
                   total = apply(df[2:6], 2, sum),
                   avgs = apply(df[2:6], 2, mean)
                   )

sampleMean <- mean(sampledf$avgs)
sampleErr <- sqrt(((10 - mean(sampledf$avgs))^2)/5)
```

### Our sample statistics for 20 flips are mean = `r sampleMean` and standard error = `r sampleErr` for this experiment.

# Analysis of flipping a fair coin fifty times.

```{r}
df1 <- tibble(n = seq(1:50),
             sample1 = rbinom(50, 1, 0.5),
             sample2 = rbinom(50, 1, 0.5),
             sample3 = rbinom(50, 1, 0.5),
             sample4 = rbinom(50, 1, 0.5),
             sample5 = rbinom(50, 1, 0.5))

groupdf1 <- melt(df1[c("sample1","sample2","sample3","sample4","sample5")], variable.name = "samplen", id.vars = 0)

ggplot(groupdf1, mapping = aes(samplen, value)) + geom_bar(stat = "identity", fill = "steelblue") + labs(x=NULL, y="Number of Heads", title = "Head Counts per Sample") + geom_hline(yintercept = 25, colour = "light gray", size = 1) + theme_minimal()

summary(df1[2:6])

sampledf1 <- tibble(n = seq(1:5),
                   total = apply(df1[2:6], 2, sum),
                   avgs = apply(df1[2:6], 2, mean)
                   )

sampleMean1 <- mean(sampledf1$avgs)
sampleErr1 <- sqrt(((25 - sampleMean1)^2)/5)
```

### Our sample statistics for 50 flips are mean = `r sampleMean1` and standard error = `r sampleErr1` for this experiment.

Comparing our mean values, we see that indeed the experiment with the higher number of observations produces a mean that is closer to the expected sample mean $\mu = np = 0.5$.
