---
title: "Experiment Results"
output: pdf_document
---

```{r include=FALSE}
library(tidyverse)
library(reshape2)

knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

```

The following table lists the results of each team member independently flipping a fair coin 20 times. An additional sample created from rbinom() is included to compare R's psuedo-random algorithm:

```{r}
resultsdf <- tibble(
  name = c("Katelyn", "Laura", "Devin", "Cole", "Lee", "R Simulation"),
  heads = c(13, 13, 11, NaN, NaN, 9),
  tails = c(7, 7, 9, NaN, NaN, 11),
  percentHeads = heads/20,
  trialError = sqrt((10 - heads)^2)
)

sampleMean <- mean(resultsdf$heads)
sampleErr <- sqrt(((10 - sampleMean)^2)/6)

knitr::kable(resultsdf, align = c('c','c','c','c','c','c'), format="pandoc", caption = "Table of Results (0 = Tails, 1 = Heads)")

ggplot(resultsdf, mapping = aes(name, heads)) + geom_bar(stat = "identity", fill = "steelblue") + labs(x=NULL, y="Number of Heads", title = "Head Counts per Sample") + geom_hline(yintercept = 10, colour = "light gray", size = 1) + theme_minimal()

summary(resultsdf$heads)
```

Here we are interested in the number of heads that appear and each of the 6 independent trials are binomially distributed with $n = 20$ and $p= 0.5$. Our sample mean $\bar{x}=$ `r sampleMean` and sample error is $\sigma_{\bar{x}} =$ `r sampleErr`.